Notes on area-length problem for CLE

### 2014-04-04 area-length/notes.tex
Gravitational dressings+one point function

Note that self-avoiding walks is the model with $\kappa=\frac{8}{3}$, $c=0$,
$e_{0}=\frac{1}{\sqrt{6}}$, $b=\sqrt{\frac{3}{2}}$ or $b=\sqrt{\frac{2}{3}}$. Since in paper
\cite{kostov2004boundary} $b$ is assumed to be less than $1$, we will use
\begin{equation}
  \label{eq:166}
  b=\sqrt{\frac{2}{3}}, \quad 0<b<1
\end{equation}
Matter theory is just a free boson, so primary fields are vertex electric and magnetic operators
\eqref{eq:135} (with the change of notations $\alpha\to \sqrt{2} e$, $2\alpha_{0}\to  e_{0}$). In
quantum gravity vertex operators are dressed by Liouville field
\begin{equation}
  \label{eq:167}
  V_{e,\alpha}(z,\bar z)=e^{2ie\chi(z,\bar z)} e^{2\alpha\varphi(z,\bar z)}
\end{equation}
in such a way that conformal dimension $\Delta=1$:
\begin{equation}
  \label{eq:168}
  e(e-e_{0})+\alpha(Q-\alpha)=1
\end{equation}
Similarly for magnetic (vortex) operators we have
\begin{equation}
  \label{eq:169}
  \chi(z,\bar z)=\chi(z)+\bar\chi(\bar z),\quad \tilde\chi(z,\bar z)=\chi(z)-\bar\chi(\bar z)
\end{equation}
\begin{equation}
  \label{eq:170}
  V_{m,\alpha}(z,\bar z)=e^{2im\tilde\chi(z,\bar z)} e^{2\alpha\varphi(z,\bar z)}
\end{equation}
Since left and right conformal dimensions
\begin{equation}
  \label{eq:171}
  \Delta_{m}=m(m-e_{0}), \quad \bar\Delta_{m}=m(m+e_{0})
\end{equation}
are not equal the field is not spinless. So we need to consider mixed operator $\mathcal{O}_{e,m}$
with dimensions \eqref{eq:134}
\begin{equation}
  \label{eq:172}
  \Delta_{e,m}=(e+m)(e+m-e_{0}), \quad \bar \Delta_{e,m}=(e-m)(e-m-e_{0})
\end{equation}
The spin $\Delta-\bar\Delta$ vanishes if $e=\frac{e_{0}}{2}$.
\begin{equation}
  \label{eq:173}
  \Delta_{\frac{e_{0}}{2},m}=m^{2}-\frac{e_{0}^{2}}{4}
\end{equation}

@@

>>>>

Note that self-avoiding walks is the model with $\kappa=\frac{8}{3}$, $c=0$,
$e_{0}=\frac{1}{\sqrt{6}}$, $b=\sqrt{\frac{3}{2}}$ or $b=\sqrt{\frac{2}{3}}$. Since in paper
\cite{kostov2004boundary} $b$ is assumed to be less than $1$, we will use
\begin{equation}
  \label{eq:166}
  b=\sqrt{\frac{2}{3}}, \quad 0<b<1
\end{equation}
Matter theory is just a free boson, so primary fields are vertex electric and magnetic operators
\eqref{eq:135} (with the change of notations $\alpha\to \sqrt{2} e$, $2\alpha_{0}\to  e_{0}$). In
quantum gravity vertex operators are dressed by Liouville field
\begin{equation}
  \label{eq:167}
  V_{e,\alpha}(z,\bar z)=e^{2ie\chi(z,\bar z)} e^{2\alpha\varphi(z,\bar z)}
\end{equation}
in such a way that conformal dimension $\Delta=1$:
\begin{equation}
  \label{eq:168}
  e(e-e_{0})+\alpha(Q-\alpha)=1
\end{equation}
Proper dressing corresponds to the choice of smaller value of $\alpha$ such that \eqref{eq:168}
holds.

Similarly for magnetic (vortex) operators we have
\begin{equation}
  \label{eq:169}
  \chi(z,\bar z)=\chi(z)+\bar\chi(\bar z),\quad \tilde\chi(z,\bar z)=\chi(z)-\bar\chi(\bar z)
\end{equation}
\begin{equation}
  \label{eq:170}
  V_{m,\alpha}(z,\bar z)=e^{2im\tilde\chi(z,\bar z)} e^{2\alpha\varphi(z,\bar z)}
\end{equation}
Since left and right conformal dimensions
\begin{equation}
  \label{eq:171}
  \Delta_{m}=m(m-e_{0}), \quad \bar\Delta_{m}=m(m+e_{0})
\end{equation}
are not equal the field is not spinless. So we need to consider mixed operator $\mathcal{O}_{e,m}$
with dimensions \eqref{eq:134}
\begin{equation}
  \label{eq:172}
  \Delta_{e,m}=(e+m)(e+m-e_{0}), \quad \bar \Delta_{e,m}=(e-m)(e-m-e_{0})
\end{equation}
The spin $\Delta-\bar\Delta$ vanishes if $e=\frac{e_{0}}{2}$.
\begin{equation}
  \label{eq:173}
  \Delta_{\frac{e_{0}}{2},m}=m^{2}-\frac{e_{0}^{2}}{4}
\end{equation}

@@

Pinning operator corresponds to $r=0, s=1$, so $m=\frac{b}{2}$ and
$\Delta=\frac{b^{2}}{4}-\frac{e_{0}^{2}}{4}=\frac{1}{2}-\frac{b^{2}}{4}$.

Dressing dimension $\alpha$ is $\frac{b}{2}$ or $\frac{1}{b}+\frac{b}{2}$, dimension of Liouville
vertex operator is $\Delta_{01}^{L}=\alpha(Q-\alpha)=\frac{1}{2}+\frac{b^{2}}{4}=\frac{1}{2}d_{H}$.

Matter field $\chi$ should satisfy some boundary condition. In Coulomb gas approach there are two
possible choices -- Dirichlet 
\begin{equation}
  \label{eq:177}
  (\partial+\bar \partial)\chi=0
\end{equation}
and Neumann
\begin{equation}
  \label{eq:178}
  (\partial-\bar \partial)\chi=0  
\end{equation}
If we want to interpret critical curves as the level lines of matter field $\chi$ we need to impose
Dirichlet conditions \eqref{eq:140}. Dirichlet condition means that field on the boundary has
constant value $\chi_{B}$.

Boundary matter fields are boundary condition changing operators between different boundary
conditions. Neumann-Neumann operators are boundary vertex operators $B_{e}=e^{ie\chi(x)}$, with
scaling dimension $\Delta^{B}_{e}=e(e-e_{0})$. Dirichlet-Dirichlet fields are boundary magnetic
operators $\tilde B_{m}$ which introduce jump $\delta\chi=2\pi m$ of the boundary value of
the field from $\chi_{B}$ to $\chi_{B}+\delta\chi_{B}=\chi_{B}+2\pi m n$. The dimension is
$\Delta^{B}_{m}=m(m-e_{0})$. Unlike the bulk magnetic operator boundary operator does not have
electric charge. Electric and magnetic charges for degenerate boundary operators are
\begin{equation}
  \label{eq:143}
  e_{rs}=\frac{1}{2}\left( e_{0}-\frac{r}{b}+sb\right),\quad m_{rs}=\frac{1}{2}\left(e_{0}-\frac{r}{b}+sb\right)
\end{equation}
Dirichlet-Neumann and Neumann-Dirichlet operators are boundary twist operators.

Wrong dressing of the identity boundary operator is $e^{\frac{\varphi}{b}}$. In this case
$\mu_{B}\sim \mu^{\frac{1}{2b^{2}}}$ and boundary is fractal. 
Two dressings are dual to each other, so if fractal boundary $\mu_{B}\sim \mu^{\frac{1}{2b^{2}}}$ corresponds to
Dirichlet boundary condition, then simple boundary $\mu_{B}\sim \mu^{\frac{1}{2}}$ corresponds to
Neumann boundary condition.

For degenerate operator $0,1$ we have $m_{01}=\frac{1}{2}\left(e_{0}+b\right)=\frac{1}{2b}$,
$\Delta^{B}_{m}=\frac{1}{2b}\left(\frac{1}{2b}-\frac{1}{b}+b\right)=\frac{1}{2}-\frac{1}{4b^{2}}$
with dressing field $B_{\beta}=e^{\beta\varphi}$ with $\beta=\frac{1}{2b}$.

The observables in two-dimensional quantum gravity are products of CFT correlation functions and
correlation functions of dressed matter vertex operators. Coordinate-independent parts of these
correlation functions are identified with restricted partition functions in microscopic models
\cite{kostov2004boundary,kostov2003boundary}. Microscopic models for quantum gravity are integrable
lattice models, such as Ising, Potts, $O(n)$ or SOS, considered on random lattices.

Bulk one-point function
\begin{equation}
  \label{eq:179}
  \left< V_{\alpha}(z,\bar z)\right>_{\sigma}=\frac{U_{\sigma}(\alpha)}{|z-\bar z|^{2\Delta_{\alpha}}}
\end{equation}
is given by the formula
\begin{equation}
  \label{eq:180}
  U_{\sigma}(\alpha)=\frac{2}{b}\left(\pi\mu\gamma(b^{2})\right)^{\frac{Q-2\alpha}{2b}}
  \Gamma(2b\alpha-b^{2})\Gamma\left(\frac{2\alpha}{b}-\frac{1}{b^{2}}-1\right) \cos[\pi(2\alpha-Q)(2\sigma-Q)]
\end{equation}
Microscopically this function is interpreted as the partition function of the loop gas on a
punctured disk with a vertex operator $V_{\alpha}$ inserted at the puncture and Dirichlet boundary
condition with the height $\sim \sigma$.

Supposedly we need to change theory by measuring length not with $e^{b\varphi}$ or
$e^{\frac{\varphi}{b}}$ but by insertion of gravitational dressing for pinning operator
$B_{m_{01}}$, which is $e^{\frac{\varphi}{2b}}$.
